% This should be \input first thing after \begin{document}


\pagestyle{empty}

\begin{center}
  {\Huge  \thevolumetitle}

  \vspace{5mm}

  {\LARGE \thevolumesubtitle}

  \vspace{5mm}

  \today

  \vspace{5mm}

%  \titleextra
\end{center}


\begin{editornote}
Editor's Note: This document has been prepared in an ad hoc
manner to provide a summary of the scope of the LBNE project as of
January 2015. 
It pulls content from version 8 of LBNE's CDR vol 4 and includes some
changes made since 2012, with notes added; the changes may not be
reflected consistently throughout the document, as a thorough editing
pass has not been made. 
It is planned to update this document in 2015 consistent with the plan
resulting from the iIEB's efforts. 
Changes to note in particular about the current plan relative to the 2012 design include: \\
\begin{itemize}
\item House two detectors, of fiducial mass 10 kton and 30 kton,
  respectively, in separate, parallel caverns. 
  Outfit the smaller cavern as soon as possible and outfit the larger
  in a later phase of work. 
  (The 30-kton detector was not part of the 2012 design; its
  configuration, to be determined by the international collaboration,
  is not discussed in this interim report.)
\item Place the compressors for the nitrogen refrigeration system on
  the surface, and place the remainder of the refrigeration system in
  the 10-kton cavern. 
  Deliver argon and nitrogen in gas form to the smaller cavern, where
  liquification will take place.
  Liquid will be transferred to and from the detector in the 30-kton
  cavern.
\item Make detector shallower and longer. 
  Build APAs of width 2.3~m and height 6~m (2012 dimensions were 2.5~m
  $\times$ 7~m). 
  Increase the length of the 10-ton detector from 25~m to 30~m.
\item Replace the far detector prototyping plan known as LAr1 by a
  plan to build and test a prototype with full-size TPC components at
  CERN.
\end{itemize}
\end{editornote}


\cleardoublepage

\pagestyle{plain} 

\renewcommand{\familydefault}{\sfdefault}
\renewcommand{\thepage}{\roman{page}}
\setcounter{page}{1}
\cleardoublepage

\setcounter{tocdepth}{3}
\textsf{\tableofcontents}
\cleardoublepage

%For acronym list to appear just after TOC
\printnomenclature
\cleardoublepage

\textsf{\listoffigures}
\cleardoublepage

\textsf{\listoftables}
\clearpage

\iffinal\else
\textsf{\listoftodos}
\clearpage
\fi

\renewcommand{\thepage}{\arabic{page}}
\setcounter{page}{1}

\pagestyle{fancy}

% Set how header/footers look
\renewcommand{\chaptermark}[1]{%
\markboth{Chapter \thechapter:\ #1}{}}
\fancyhead{}
\fancyhead[RO,LE]{\textsf{\footnotesize \thechapter--\thepage}}
\fancyhead[LO,RE]{\textsf{\footnotesize \leftmark}}

\fancyfoot{}
\fancyfoot[RO]{\textsf{\footnotesize LBNE Conceptual Design Report}}
\fancyfoot[LE]{\textsf{\footnotesize \thevolumetitle}}
\fancypagestyle{plain}{}

\renewcommand{\headrule}{\vspace{-4mm}\color[gray]{0.5}{\rule{\headwidth}{0.5pt}}}

